Import_Map

### 2024-06-06 Code/Plots_ProNicheMap.Rmd
Map edits

```{r save plot}
ggsave(file = file.path(FigPath, paste("NichesMap",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
```

@@

@@

ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6)  +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
  coord_fixed(ratio = 2, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
  guides(color = "none") +
  theme_bw() +
  theme(plot.title = element_text(vjust = 10),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=18),
        #axis.title = element_text(size=14),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=18),
        #axis.title.y = element_text(vjust = 1),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))

>>>>

```{r save plot}
#ggsave(file = file.path(FigPath, paste("NichesMap",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
```

@@

# PhotoperiodDepthOMZ1<-PhotoperiodDepthOMZ %>% 
# filter(DayofYear == "Summer Solstice")
# PhotoperiodDepthOMZ1$nm <- c(400, 400, 700, 700)
# PhotoperiodDepthOMZ1$de <- c(400, 400, 700, 700)
# 
# PhotoperiodDepthOMZ2<-PhotoperiodDepthOMZ %>% 
# filter(DayofYear == "Winter Solstice")
# PhotoperiodDepthOMZ2$nm <- c(400, 400, 700, 700)
# 
# PhotoperiodDepthOMZ3<-PhotoperiodDepthOMZ %>% 
# filter(DayofYear == "Equinox")
# PhotoperiodDepthOMZ3$nm <- c(400, 400, 700, 700)
# 
# PhotoperiodDepthOMZss<-rbind(PhotoperiodDepthOMZ1, PhotoperiodDepthOMZ2, PhotoperiodDepthOMZ3)

@@

ggplot()+
  # stat_wl_strip(aes(x = nm), ymin = "50 m", ymax = "100 m", alpha = 0.5, PhotoperiodDepthOMZss) +
  # scale_fill_identity() +
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6)  +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
  coord_fixed(ratio = 2, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
  guides(color = "none") +
  theme_bw() +
  theme(plot.title = element_text(vjust = 10),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=18),
        #axis.title = element_text(size=14),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=18),
        #axis.title.y = element_text(vjust = 1),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
